Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-29 paper_jasa.tex
effect of null plots

%\green{Add figure showing proportion correct vs p-value of actual data plot for experiments 1 and 2.}

\green{You need to explain visual $p$-value - how is this calculated. How is this different from the signal strength. And please say why you introduce a term signal strength.}

@@

\green{Be consistent with capitalization of plot labels - check this everywhere - you have lower case signal and upper case Strength}

@@

\hh{
\subsection{How much do null plots affect the choice?}
Another difference between conventional tests and visual inference is the potential influence that null plots have on an observer's choice of plot. If one or more null plots represent data with -- by chance -- a smaller $p$-value than the data plot, there's a strong possibility that an observer will pick the null plot instead of the data plot, independently of the actual value of the $p$-value.

See figure \ref{fig:pval_difference} of evidence for this phenomenon.
%Mahbub, could you have a look at the lineups, and compute the difference between the data plot's $p$-value and the  smallest $p$ value of a null plot, and plot that in a scatterplot against proportion correct? Thanks!

This problem is further investigated in the paper \cite{waldo}.

}

@@

\green{Mention the possibility of a visual skills test, to select the workers that are better qualified, to implement the lineup protocol in practice. Along the lines of the Army tests that Susan brought to the working group.}

>>>>

@@

\green{Explain why the term ``plot signal'' is introduced}

@@

\subsection{How much do null plots affect the choice?}

Another difference between conventional tests and visual inference is that the observer's choice of plot may be influenced by the $m-1$ null plots in the lineup. We have already seen that observers tend to pick the plot with the lowest $p$-value. If one or more null plots represent data having -- by chance -- a smaller $p$-value than the actual data plot, there's a strong possibility that an observer will pick this null plot instead of the actual data plot.

Figure \ref{fig:pval_difference} investigates this for the data collected in experiments 1 and 2. The horizontal axis shows the difference between the smalles $p$-value of the null plots, and that of the actual data plot. Large values indicate that the actual data plot has a much smaller $p$-value than any of the null plots. The vertical axis shows percent subjects choosing the actual data plot. \green{Is this really pct correct, or 1-pct correct? When there is a big diff in p-value almost no-one gets it right! Maybe it is just a scale issue?} We see that when there is a big difference between the $p$-values observers choose the actual data plot more often.

%Mahbub, could you have a look at the lineups, and compute the difference between the data plot's $p$-value and the  smallest $p$ value of a null plot, and plot that in a scatterplot against proportion correct? Thanks!

This problem is further investigated in the paper \cite{waldo}. Here numerical measures of the similarity between plots are proposed to provide quality metrics for lineups.

@@

\green{Mention the possibility of a visual skills test, to select the workers that are better qualified, to implement the lineup protocol in practice. Along the lines of the Army tests that Susan brought to the working group.

Discuss the purpose of randomly generating data null plots, rather than selectively sampling from the null distribution.}
